Non-word repetition in Yélî Dnye

### 2021-01-26 manuscript.Rmd
added discussion of other lit

## TODO

1. add legend to new figure, improve color coding
1. conclusion: definitely the case that Tsi lower than others, but unclear what this is due to; some variation across samples, but since stimuli haven't been carefully matched, and ages either, we can't be totally sure there either -- also, literacy may be another issue
1. revise discussion
1. improve figure 1?

@@

```{r fig-prevlit-overall, echo = FALSE, ig.pos = "T!", fig.width=8, fig.height=5.5, fig.cap = "NWR scores as a function of age (in years). Jaber-Awida (2018) reported on 20 Arabic learners (orange); Piazzalunga et al. (2019) reported on groups of 24-60 Italian learners (black); Cristia et al. (2020) reported on groups of 4-6 Tsimane' learners (green); the present study reports on groups of 8-19 Yélî Dnye learners (purple). Central tendency is mean in Arabic and Tsimane', median in Italian and Yélî Dnye; error is one standard error. Age has been slightly jittered for ease of inspection of different lengths at a given age."}

@@

mycols = c( 
             "Arabic" = "orange",
             "Cantonese"   ="blue",
             "English"   ="green",
             "Italian"   ="black",
             "Mandarin"   ="gray",
             "Persian"   ="pink",
             "Slovak"   ="lightblue",
            "Sotho"   ="magenta",
            "Spanish"   ="yellow",
            "Swedish"   ="darkgray",
            "Tsimane'" = "darkgreen",
             "Yélî" = "purple")

@@

for(thislang in levels(factor(pl_overall$Language))) {
  myx=pl_overall$Age[pl_overall$Language==thislang ]
  myy=pl_overall$Overall[pl_overall$Language==thislang]
  lines(myy~myx, col=mycols[thislang],lwd=mywd[thislang]) #join points of same length & lang
  mylb=myy-pl_overall$se[pl_overall$Language==thislang]
  myhb=myy+pl_overall$se[pl_overall$Language==thislang]
  for(i in 1:length(mylb)) {
    mylty=as.numeric(as.character(thislength))
    lines(rep(myx[i],2),c(mylb[i],myhb[i]),col=mycols[thislang],lty=mylty) #error bar
    lines(c(myx[i]-.1,myx[i]+.1),c(mylb[i],mylb[i]),col=mycols[thislang],lty=mylty) #lower error bar tip
    lines(c(myx[i]-.1,myx[i]+.1),c(myhb[i],myhb[i]),col=mycols[thislang],lty=mylty) #higher error bar tip
    }
}

#add legend

In our sample of `r nrow(overall)` children between ages `r min(overall$Age)` and `r max(overall$Age)`, the average item-level score was `r round(mean(overall$Word))`%, falling well within the expected range of NWR applications in previous studies on a variety of linguistic populations (see Figure \@ref(fig:fig-prevlit)). Segment-based normalized Levenshtein distance  indicate that inexact repetitions often constituted _mostly_ accurate reroductions of the target, with an average of `r round(mean(overall$NLD))`% of the stimulus segments getting substituted, inserted, or deleted upon repetition. Paired with our thorough training protocol, we take these NWR scores as indicating that (a) our adaptations to NWR for this context were successful, even given a number of non-standard changes to the training phase and to the design of the stimuli and (b) Yélî children show comparable performance to others tested on a similar task, despite the many linguistic, cultural, and socioeconomic differences between this and previously tested populations. Given successful (and comparable) execution of this task.

Some portion of the errors were introduced when the participant produced a real word (in Yélî Dnye or English) in response to the stimulus. Real-word repetitions here made up two thirds of errorful repetitions---this is quite high compared to past work [e.g., @castro1998illiterate], but it is unclear what caused this pattern in the current study: Castro and colleagues' [-@castro1998illiterate] study focused on adults rather than children, the task was administered by a team including a foreign, English-speaking researcher, and the particularities of the Yélî Dnye phonological inventory result in many true-word phonetic neighbors. Follow-up work exploring this type of error in children from other populations in addition to further work on Yélî children will clarify this effect.

- despite 4-syll being rare, they are repeated correctly
- similar levels of IDS in Tsi & YD, yet very different results: overall NWR, effect of length
- conclusions Cristia about long-term effects perhaps don't hold
- or perhaps input estimation is inaccurate -- talk about different ways of estimating input quantity across papers and uncertainty in estimates
- or perhaps it's about the prevalence of literacy in the population -- phonetic effects of learning to read & consequences in young children's encoding and decoding of sounds for NWR
- differences in test: group versus individual, level of training of RA, from the same community or not, model was native or not, heard over headphones or not

>>>>

## TODO Alex

- add missing refs
- correct rest of discussion

## TODO Middy

- read over whole thing -- does the logic sound ok?
- if you are motivated to, improve figures 1 and 5 (integrating our results to previous lit) -- but I also think we can submit the paper with these figures as they are, and propose improvements in a revision

@@

```{r prep-pl}

@@

all_lang=levels(factor(pl_overall$Language))

One of the questions in our mind when designing this study was whether NWR was a fair test of phonological development across languages and cultures. Although our data cannot answer this question because we have only sampled one language and culture here, we would like to spend some time discussing the integration of these results to the wider NWR literature. It is important to note at the outset that we cannot obtain a final answer because integration across studies implies not only variation in languages and child-rearing settings, but also in methodological aspects including non-word length, non-word design (e.g., the syllable and phone complexity included in the items), and task administration, among others. Nonetheless, we feel the NWR task is prevalent enough to warrant discussion about this, as it is done for other tasks sometimes used to describe and compare children's language skills across populations, like the MacArthur-Bates Communicative Development Inventory [@wordbank].

At first sight, when we had compared our results to those of other studies, we thought the range of performance we observed overlapped with previously observed levels of performance.  Paired with our thorough training protocol, we had interpreted the NWR scores among Yélî Dnye learners as indicating that our adaptations to NWR for this context were successful, even given a number of non-standard changes to the training phase and to the design of the stimuli. Additionally, it seemed that Yélî children show edcomparable performance to others tested on a similar task, despite the many linguistic, cultural, and socioeconomic differences between this and previously tested populations, unlike the case that had been reported for the Tsimane'.

To enrich this discussion, we looked for previous studies on monolingual children with normative development learning diverse languages, and entered them when they reported non-word repetition scores based on whole item scoring. We entered data from `r length(levels(pl_overall$Study))` studies (including ours), presenting data from `r length(all_lang)` languages. Specifically, Arabic was represented by @jabere2018xperiment; Cantonese by @stokes; English by @vance2005speech; Italian by @piazzalunga2019articulatory; Mandarin by @lei; Persian by @farmani2018normalization; Slovak by @kapalkova and @polisenska; Sotho by @wilsenach2013phonological; Spanish by @balladares2016socio; Swedish by @kalnak2014nonword and @Radeborg; Tsimane' by @cristia2020infant; and Yélî Dnye by the present study. Studies varied in the length of non-words that were considered; whenever results were reported separately for different lengths, we calculated overall averages based on lengths of 2 and 3 syllables, for increased comparability. Results separating different age groups are shown in \@ref(fig:fig-prevlit-overall).

```{r fig-prevlit-overall, echo = FALSE, ig.pos = "T!", fig.width=8, fig.height=5.5, fig.cap = "NWR scores as a function of age (in years), averaged across multiple non-word lengths, as a function of children's native languages. The legend indicates language and the length of non-words (in syllables). Central tendency is mean; error is one standard error."}
mycols = c( 
             "Arabic" = "orange",
             "Cantonese"   ="blue",
             "English"   ="green",
             "Italian"   ="black",
             "Mandarin"   ="gray",
             "Persian"   ="pink",
             "Slovak"   ="lightblue",
            "Sotho"   ="magenta",
            "Spanish"   ="brown",
            "Swedish"   ="darkgray",
            "Tsimane'" = "darkgreen",
             "Yélî" = "purple")

@@

for(thislang in levels(factor(pl_overall$Language))) {
  myx=pl_overall$Age[pl_overall$Language==thislang ]
  myy=pl_overall$Overall[pl_overall$Language==thislang]
  lines(myy~myx, col=mycols[thislang],lwd=mywd[thislang]) #join points of same length & lang
  mylb=myy-pl_overall$se[pl_overall$Language==thislang]
  myhb=myy+pl_overall$se[pl_overall$Language==thislang]
  for(i in 1:length(mylb)) {

    lines(rep(myx[i],2),c(mylb[i],myhb[i]),col=mycols[thislang]) #error bar
    lines(c(myx[i]-.1,myx[i]+.1),c(mylb[i],mylb[i]),col=mycols[thislang]) #lower error bar tip
    lines(c(myx[i]-.1,myx[i]+.1),c(myhb[i],myhb[i]),col=mycols[thislang]) #higher error bar tip
    }
}

#add legend
#first half of langs
xmin=6
ymax=30
ymin=0
myy=seq(from=ymax,to=ymin,length.out=length(all_lang)/2)
names(myy)<-all_lang[1:(length(all_lang)/2)]
for(thislang in names(myy)){
  lines(c(xmin-.1,xmin+.1),c(myy[thislang],myy[thislang]),col=mycols[thislang]) #line sample
  text(xmin+.15,myy[thislang],paste(thislang,pl_overall$Lengths[pl_overall$Language==thislang][1]),col=mycols[thislang],pos=4)
}

#second half
xmin=9.5
names(myy)<-all_lang[(length(all_lang)/2+1):length(all_lang)]
for(thislang in names(myy)){
  lines(c(xmin-.1,xmin+.1),c(myy[thislang],myy[thislang]),col=mycols[thislang]) #line sample
  text(xmin+.15,myy[thislang],paste(thislang,pl_overall$Lengths[pl_overall$Language==thislang][1]),col=mycols[thislang],pos=4)
} 
```

Several observations can be drawn from this Figure. To begin with, we focus on the comparison between Yélî Dnye and Tsimane'. These two groups have been described as having roughly similar levels of child-directed speech, yet they exhibit very different results, with lower overall NWR scores and (integrating with effect of length in  \@ref(fig:fig-prevlit-overall)) length effects. This may indicate that the conclusion tentatively drawn in @cristia2020infant about lower NWR scores consistent with long-term effects of lower levels of child-directed speech was premature. Naturally, there is an alternative interpretation, namely that input estimation suggesting very slightly higher levels of child-directed speech among the Tsimane' than among Yélî Dnye learners is inaccurate. In fact, careful reading of previous reports highlight important methodological differences in how input quantity has been estimated across papers: @casillas2020early hand-coded speech with the help of a native research assistant, and then summed all child-directed speech, which effectively establishes an upper boundary of the speech children could potentially process. @cristia estimated quantities from behavioral observations on the frequency of child-directed one-on-one conversation, which is probably closer to a lower boundary. Finally, @scaff2021daylong used human annotation for detecting speech but an automated temporal method for assigning speech as child-directed or not, in a way that could lead to over-estimation (because any speech by e.g. a female adult that was not temporally close to speech by others would count as child-directed). A final answer to the question of how much child-directed speech is afforded to Yélî and Tsimane' children must await fully comparable methods.

That said, @cristia2020infant also pointed out another characteristic of the Tsimane' culture, and this was the relatively low prevalence of literacy, and generally the variable access to formal education. This is a very different case from the Yélî population studied here, where all adults have accumulated several years of schooling, and literacy is widespread. If this second hypothesis holds, then this may mean that there are phonetic effects of learning to read in the input afforded to young children, and that this has consequences for young children's encoding and decoding of sounds in the context of NWR tasks. Notice that this is not the same as the oft-recorded effect of learning to read affecting NWR performance, illustrated for instance in the data for Sotho in \@ref(fig:fig-prevlit-overall). These two data points have been gathered from two groups of children, all exposed mainly to Sotho, but children with higher NWR had been learning to read in Sotho, whereas those with lower scores were learning to read in English. What is at stake in the second interpretation of the lower scores observed among the Tsimane' is related  to literacy *in the broader population* (rather than in the tested children themselves).

Although exciting, this hypothesis is only one of many. Another plausible explanation is that the Tsimane' results are not comparable to the previous body of literature, and specifically to our study. @cristia2020infant administered the NWR in the form of a group game played outside, with a non-native experimenter providing the target, and each person of the group attempting it in their stead. This immediately means a number of important methodological differences with the standard implementation of NWR, where children are tested individually, they hear items spoken by a native speaker (often over headphones), the experimenter tends to belong to the same community as the children, and testing occurs in quiet conditions (with little background noise). Thus, a priority is for additional data gathered using this more novel testing paradigm in other populations, or from the Tsimane' using the more traditional paradigm.

Broadening our discussion to all of the studies in our literature review, we notice that there is rather wide variation of the range of NWR scores found across these samples, as well as the strength of age effects. We performed some exploratory analyses to see whether features of the languages children were learning could be related to their overall NWR scores. We extracted the number of phonemes in the language from PHOIBLE and coded whether words in the language tended to be longer or shorter based on information in the papers or other sources. Neither of these two predictors explained variance  in \@ref(fig:fig-prevlit-overall). It is possible that average word length plays a role, but often researchers incorporate this into their design by including longer items when the native language allows this, with e.g. Sotho non-words having 4-7 syllables in length. To be more certain whether language characteristics do account for meaningful variation in NWR scores, it will be necessary to design NWR tasks that are cross-linguistically valid. We believe this will be excedingly difficult (or perhaps impossible), since it would entail defining a 10-20 set of items that are meaningless in all of the languages as well as phonotactically legal. An alternative may be to find ways to regress out some of these effects, and thus compare languages while controlling for choices of phonemes, syllable structure, and overall length of the NWR items.

### Additional observations

Some portion of the errors were introduced when the participant produced a real word (in Yélî Dnye or English) in response to the stimulus. Real-word repetitions here made up two thirds of errorful repetitions---this is quite high compared to past work [e.g., @castro1998illiterate], but it is unclear what caused this pattern in the current study: Castro and colleagues' [-@castro1998illiterate] study focused on adults rather than children, the task was administered by a team including a foreign, English-speaking researcher, and the particularities of the Yélî Dnye phonological inventory result in many true-word phonetic neighbors. Follow-up work exploring this type of error in children from other populations in addition to further work on Yélî children may clarify this effect.

### 2021-01-26 manuscript.tex
added discussion of other lit

\hypertarget{todo}{%
\subsection{TODO}\label{todo}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  add legend to new figure, improve color coding
\item
  conclusion: definitely the case that Tsi lower than others, but unclear what this is due to; some variation across samples, but since stimuli haven't been carefully matched, and ages either, we can't be totally sure there either -- also, literacy may be another issue
\item
  revise discussion
\item
  improve figure 1?
\end{enumerate}

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/fig-prevlit-overall-1.pdf}
\caption{\label{fig:fig-prevlit-overall}NWR scores as a function of age (in years). Jaber-Awida (2018) reported on 20 Arabic learners (orange); Piazzalunga et al. (2019) reported on groups of 24-60 Italian learners (black); Cristia et al. (2020) reported on groups of 4-6 Tsimane' learners (green); the present study reports on groups of 8-19 Yélî Dnye learners (purple). Central tendency is mean in Arabic and Tsimane', median in Italian and Yélî Dnye; error is one standard error. Age has been slightly jittered for ease of inspection of different lengths at a given age.}
\end{figure}

In our sample of 40 children between ages 3 and 10, the average item-level score was 65\%, falling well within the expected range of NWR applications in previous studies on a variety of linguistic populations (see Figure \ref{fig:fig-prevlit}). Segment-based normalized Levenshtein distance indicate that inexact repetitions often constituted \emph{mostly} accurate reroductions of the target, with an average of 21\% of the stimulus segments getting substituted, inserted, or deleted upon repetition. Paired with our thorough training protocol, we take these NWR scores as indicating that (a) our adaptations to NWR for this context were successful, even given a number of non-standard changes to the training phase and to the design of the stimuli and (b) Yélî children show comparable performance to others tested on a similar task, despite the many linguistic, cultural, and socioeconomic differences between this and previously tested populations. Given successful (and comparable) execution of this task.

Some portion of the errors were introduced when the participant produced a real word (in Yélî Dnye or English) in response to the stimulus. Real-word repetitions here made up two thirds of errorful repetitions---this is quite high compared to past work (e.g., Castro-Caldas et al., 1998), but it is unclear what caused this pattern in the current study: Castro and colleagues' (1998) study focused on adults rather than children, the task was administered by a team including a foreign, English-speaking researcher, and the particularities of the Yélî Dnye phonological inventory result in many true-word phonetic neighbors. Follow-up work exploring this type of error in children from other populations in addition to further work on Yélî children will clarify this effect.

\begin{itemize}
\tightlist
\item
  despite 4-syll being rare, they are repeated correctly
\item
  similar levels of IDS in Tsi \& YD, yet very different results: overall NWR, effect of length
\item
  conclusions Cristia about long-term effects perhaps don't hold
\item
  or perhaps input estimation is inaccurate -- talk about different ways of estimating input quantity across papers and uncertainty in estimates
\item
  or perhaps it's about the prevalence of literacy in the population -- phonetic effects of learning to read \& consequences in young children's encoding and decoding of sounds for NWR
\item
  differences in test: group versus individual, level of training of RA, from the same community or not, model was native or not, heard over headphones or not
\end{itemize}

@@

\leavevmode\hypertarget{ref-casillas2020early}{}%
Casillas, M., Brown, P., \& Levinson, S. C. (2020). Early language experience in a papuan community. \emph{Journal of Child Language}, \emph{XX}, XX--XX.

>>>>

\hypertarget{todo-alex}{%
\subsection{TODO Alex}\label{todo-alex}}

\begin{itemize}
\tightlist
\item
  add missing refs
\item
  correct rest of discussion
\end{itemize}

\hypertarget{todo-middy}{%
\subsection{TODO Middy}\label{todo-middy}}

\begin{itemize}
\tightlist
\item
  read over whole thing -- does the logic sound ok?
\item
  if you are motivated to, improve figures 1 and 5 (integrating our results to previous lit) -- but I also think we can submit the paper with these figures as they are, and propose improvements in a revision
\end{itemize}

@@

One of the questions in our mind when designing this study was whether NWR was a fair test of phonological development across languages and cultures. Although our data cannot answer this question because we have only sampled one language and culture here, we would like to spend some time discussing the integration of these results to the wider NWR literature. It is important to note at the outset that we cannot obtain a final answer because integration across studies implies not only variation in languages and child-rearing settings, but also in methodological aspects including non-word length, non-word design (e.g., the syllable and phone complexity included in the items), and task administration, among others. Nonetheless, we feel the NWR task is prevalent enough to warrant discussion about this, as it is done for other tasks sometimes used to describe and compare children's language skills across populations, like the MacArthur-Bates Communicative Development Inventory ({\textbf{???}}).

At first sight, when we had compared our results to those of other studies, we thought the range of performance we observed overlapped with previously observed levels of performance. Paired with our thorough training protocol, we had interpreted the NWR scores among Yélî Dnye learners as indicating that our adaptations to NWR for this context were successful, even given a number of non-standard changes to the training phase and to the design of the stimuli. Additionally, it seemed that Yélî children show edcomparable performance to others tested on a similar task, despite the many linguistic, cultural, and socioeconomic differences between this and previously tested populations, unlike the case that had been reported for the Tsimane'.

To enrich this discussion, we looked for previous studies on monolingual children with normative development learning diverse languages, and entered them when they reported non-word repetition scores based on whole item scoring. We entered data from 14 studies (including ours), presenting data from 12 languages. Specifically, Arabic was represented by Jaber-Awida (2018); Cantonese by ({\textbf{???}}); English by Vance et al. (2005); Italian by Piazzalunga et al. (2019); Mandarin by ({\textbf{???}}); Persian by Farmani et al. (2018); Slovak by ({\textbf{???}}) and ({\textbf{???}}); Sotho by Wilsenach (2013); Spanish by Balladares et al. (2016); Swedish by Kalnak et al. (2014) and ({\textbf{???}}); Tsimane' by Cristia et al. (2020); and Yélî Dnye by the present study. Studies varied in the length of non-words that were considered; whenever results were reported separately for different lengths, we calculated overall averages based on lengths of 2 and 3 syllables, for increased comparability. Results separating different age groups are shown in \ref{fig:fig-prevlit-overall}.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/fig-prevlit-overall-1.pdf}
\caption{\label{fig:fig-prevlit-overall}NWR scores as a function of age (in years), averaged across multiple non-word lengths, as a function of children's native languages. The legend indicates language and the length of non-words (in syllables). Central tendency is mean; error is one standard error.}
\end{figure}

Several observations can be drawn from this Figure. To begin with, we focus on the comparison between Yélî Dnye and Tsimane'. These two groups have been described as having roughly similar levels of child-directed speech, yet they exhibit very different results, with lower overall NWR scores and (integrating with effect of length in \ref{fig:fig-prevlit-overall}) length effects. This may indicate that the conclusion tentatively drawn in Cristia et al. (2020) about lower NWR scores consistent with long-term effects of lower levels of child-directed speech was premature. Naturally, there is an alternative interpretation, namely that input estimation suggesting very slightly higher levels of child-directed speech among the Tsimane' than among Yélî Dnye learners is inaccurate. In fact, careful reading of previous reports highlight important methodological differences in how input quantity has been estimated across papers: Casillas et al. (2020) hand-coded speech with the help of a native research assistant, and then summed all child-directed speech, which effectively establishes an upper boundary of the speech children could potentially process. ({\textbf{???}}) estimated quantities from behavioral observations on the frequency of child-directed one-on-one conversation, which is probably closer to a lower boundary. Finally, Scaff et al. (2021) used human annotation for detecting speech but an automated temporal method for assigning speech as child-directed or not, in a way that could lead to over-estimation (because any speech by e.g.~a female adult that was not temporally close to speech by others would count as child-directed). A final answer to the question of how much child-directed speech is afforded to Yélî and Tsimane' children must await fully comparable methods.

That said, Cristia et al. (2020) also pointed out another characteristic of the Tsimane' culture, and this was the relatively low prevalence of literacy, and generally the variable access to formal education. This is a very different case from the Yélî population studied here, where all adults have accumulated several years of schooling, and literacy is widespread. If this second hypothesis holds, then this may mean that there are phonetic effects of learning to read in the input afforded to young children, and that this has consequences for young children's encoding and decoding of sounds in the context of NWR tasks. Notice that this is not the same as the oft-recorded effect of learning to read affecting NWR performance, illustrated for instance in the data for Sotho in \ref{fig:fig-prevlit-overall}. These two data points have been gathered from two groups of children, all exposed mainly to Sotho, but children with higher NWR had been learning to read in Sotho, whereas those with lower scores were learning to read in English. What is at stake in the second interpretation of the lower scores observed among the Tsimane' is related to literacy \emph{in the broader population} (rather than in the tested children themselves).

Although exciting, this hypothesis is only one of many. Another plausible explanation is that the Tsimane' results are not comparable to the previous body of literature, and specifically to our study. Cristia et al. (2020) administered the NWR in the form of a group game played outside, with a non-native experimenter providing the target, and each person of the group attempting it in their stead. This immediately means a number of important methodological differences with the standard implementation of NWR, where children are tested individually, they hear items spoken by a native speaker (often over headphones), the experimenter tends to belong to the same community as the children, and testing occurs in quiet conditions (with little background noise). Thus, a priority is for additional data gathered using this more novel testing paradigm in other populations, or from the Tsimane' using the more traditional paradigm.

Broadening our discussion to all of the studies in our literature review, we notice that there is rather wide variation of the range of NWR scores found across these samples, as well as the strength of age effects. We performed some exploratory analyses to see whether features of the languages children were learning could be related to their overall NWR scores. We extracted the number of phonemes in the language from PHOIBLE and coded whether words in the language tended to be longer or shorter based on information in the papers or other sources. Neither of these two predictors explained variance in \ref{fig:fig-prevlit-overall}. It is possible that average word length plays a role, but often researchers incorporate this into their design by including longer items when the native language allows this, with e.g.~Sotho non-words having 4-7 syllables in length. To be more certain whether language characteristics do account for meaningful variation in NWR scores, it will be necessary to design NWR tasks that are cross-linguistically valid. We believe this will be excedingly difficult (or perhaps impossible), since it would entail defining a 10-20 set of items that are meaningless in all of the languages as well as phonotactically legal. An alternative may be to find ways to regress out some of these effects, and thus compare languages while controlling for choices of phonemes, syllable structure, and overall length of the NWR items.

\hypertarget{additional-observations}{%
\subsubsection{Additional observations}\label{additional-observations}}

Some portion of the errors were introduced when the participant produced a real word (in Yélî Dnye or English) in response to the stimulus. Real-word repetitions here made up two thirds of errorful repetitions---this is quite high compared to past work (e.g., Castro-Caldas et al., 1998), but it is unclear what caused this pattern in the current study: Castro and colleagues' (1998) study focused on adults rather than children, the task was administered by a team including a foreign, English-speaking researcher, and the particularities of the Yélî Dnye phonological inventory result in many true-word phonetic neighbors. Follow-up work exploring this type of error in children from other populations in addition to further work on Yélî children may clarify this effect.

@@

\leavevmode\hypertarget{ref-casillas2020early}{}%
Casillas, M., Brown, P., \& Levinson, S. C. (2020). Early language experience in a Papuan community. \emph{Journal of Child Language}, \emph{XX}, XX--XX.
